The MACE is essentially unidimensional: Bifactor models of the `Maltreatment and Abuse Chronology of Exposure' scale

### 2022-07-30 manuscript/main.tex
updated supp figs; updated naming conventions; more manuscript edits

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}

@@

Using the cutoffs recommended by \cite{hidalgo2014binary}, we identified 11 of 52 items on the MACE that exhibited large DIF by study (Figure S1). Interestingly these included all six of the reverse-scored items. We also found an additional 11 items that exhibited large DIF by gender (Figure S2). Five of these items concerned sexual abuse (endorsed by more women than men), and another five concerned peer physical abuse (endorsed by more men than women). We identified no items that exhibited large DIF by age. Given the number of items exhibiting DIF by sample membership, we elected to model each sample separately.

@@

>>>>

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\usepackage{setspace}

@@

Using the cutoffs recommended by \cite{hidalgo2014binary}, we identified 11 of 52 items on the MACE that exhibited large DIF by study (Figure \ref{fig:dif_study}). Interestingly these included all six of the reverse-scored items. We also found an additional 11 items that exhibited large DIF by gender (Figure \ref{fig:dif_gender}). Five of these items concerned sexual abuse (endorsed by more women than men), and another five concerned peer physical abuse (endorsed by more men than women). We identified no items that exhibited large DIF by age. Given the number of items exhibiting DIF by sample membership, we elected to model each sample separately.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.82\textwidth,center]{figures/figS01.png}
    \caption{\normalfont \begin{spacing}{1.25} Differential item functioning by sample. (A) Proportions of participants endorsing having experienced a maltreatment event by study sample. (B) The log odds that the proportion of endorsements are larger in one or the other sample. Dotted lines indicate the threshold for large DIF recommended by \cite{hidalgo2014binary}. ** Reverse-scored items \end{spacing}}
    \label{fig:dif_study}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.82\textwidth,center]{figures/figS02.png}
    \caption{\normalfont \begin{spacing}{1.25} Differential item functioning by gender. (A) Proportions of participants endorsing having experienced a maltreatment event by study gender. (B) The log odds that the proportion of endorsements are larger in one or the other gender. Dotted lines indicate the threshold for large DIF recommended by \cite{hidalgo2014binary}. ** Reverse-scored items \end{spacing}}
    \label{fig:dif_gender}
\end{figure}
